Americans who are wealthier and perform more strength training are less likely to be obese\thanks{Code and data are available at: https://github.com/bestmustard/activity-bmi}

### 2024-04-19 paper/paper.tex
completed

\KOMAoption{captions}{tableheading}
\usepackage{float} \floatplacement{figure}{H}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Physical activity is as tied to obesity as we expect it to be},
  pdfauthor={Victor Ma},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Physical activity is as tied to obesity as we expect it to
be\thanks{Code and data are available at:
https://github.com/bestmustard/activity-bmi}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{An analysis of American exerise habits and their BMI}
\author{Victor Ma}
\date{March 16, 2024}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

The data I am using is from the Center of Disease Control and Prevention
(CDC), a government-officiated service organization dedicated to health
research in the United States. In particular, this dataset contains
information on an adult's diet, physical activity, and weight status
from CDC's Behavioral Risk Factor Surveillance System- America's premier
system for collecting data about health-related risk behaviours
conducted through telephone surveys (Centers for Disease Control and
Prevention (CDC), National Center for Chronic Disease Prevention and
Health Promotion, Division of Nutrition, Physical Activity, and Obesity
2023). I will be focusing on the variables of activity level and level
of income as explanatory variables in the logistic regression model. The
estimand will be the probability that an individual is obese based on
these factors.

@@

This analysis is conducted using R, using several R packages to
facilitate my analysis and presentation. This includes tidyverse for
data manipulation and visualization, knitr for report generation,
modelsummary for model interpretation, and rstanarm for Bayesian
regression modeling (R Core Team 2021; \textbf{Dataverse?}; Xie 2021;
Arel-Bundock 2021; Goodrich et al. 2022; Kay 2021; Wickham et al. 2021).
Some portions including ggplot graphs and the ``Discussion'' section
were written with the help of ChatGPT4 OpenAI (2023). \newpage

@@

I used a dataset called ``Nutrition, Physical Activity, and Obesity -
Behavioral Risk Factor Surveillance System'' pulled directly from the
CDC website (Centers for Disease Control and Prevention (CDC), National
Center for Chronic Disease Prevention and Health Promotion, Division of
Nutrition, Physical Activity, and Obesity 2023). The .csv file obtained
from the website contains 93250 data points with the relevant
information of an individual's activity level based on their survey
response, BMI, and various demographics. The dataset is owned by the
Division of Nutrition, Physical Activity, Obesity (DNPAO), a division
under the CDC which focuses directly on preventing chronic diseases by
promoting better nutrition practices.

\hypertarget{source-reliability}{%
\subsection{Source Reliability}\label{source-reliability}}

The Centers for Disease Control and Prevention (CDC) is recognized as a
reliable source for obesity data for several reasons. The CDC's Division
of Nutrition, Physical Activity, and Obesity conducts comprehensive
surveillance and research to understand and address obesity, focusing on
policy and environmental strategies to promote healthy eating and active
living. The organization collects data from the largest scale health
survey systems in the United States, including both the Behavioral Risk
Factor Surveillance System (BRFSS) and the National Health and Nutrition
Examination Survey (NHANES) ({``Data \& Statistics \textbar{} Overweight
\& Obesity \textbar{} CDC,''} n.d.; {``Overweight \& Obesity \textbar{}
CDC,''} n.d.).

The BRFSS conducts more than 400,000 interviews annually across the
United States, offering state-level estimates of obesity prevalence
among other health parameters. The large sample size it offers provides
a better understanding of the population when compared to smaller
samples ({``4 Comparison of Data Sources Used to Assess Obesity
Prevalence and Trends,''} n.d.).

@@

The data used in this paper does not represent the full dataset, as data
points had to be removed for any missing responses. The previously more
robust dataset with 93250 data points was reduced to 10218 in this
process. The categories available for both the respondent variables do
not allow for some details, as the markers for physical activity were
very specific. Many individuals may not adhere directly to the possible
responses in the survey, and it is impossible to account for individuals
who perform more physiccal activity than the provided options. The
income levels also do not provide a broad perspective, with the maximum
level being \$75,000+. There is no evidence or rationale provided
regarding why these options were chosen.

@@

Figure~\ref{fig-activity} tells us that 4-year degree graduates are the
most well represented in the polls, followed by high school graduates,
people with some college, and then 2-year degree graduates. People who
have not graduated high school are hardly represented at all.

In Figure~\ref{fig-income} we see 45-64 being the most dominant age
group, with much less representation in the 18-29 range. Also, about
20\% more females participated in the study than males.

Below are some figures representing who people voted for based on their
age and gender, followed by education level and gender.

@@

Figure~\ref{fig-activityobesity} shows a negative correlation between
votes for Joe Biden and older age groups.

@@

We can see that in \textbf{?@fig-gendervotes}, more women voted for Joe
Biden than men.

@@

In order to better interpret the results of the model, I can create a
coefficient plot to visually see the effect sizes of the predictor
variables on the likelihood of an individual supporting Biden.

Figure~\ref{fig-coefficient} maps each predictor variable on the y-axis
to an effect size and confidence interval on the x-axis. The effect size
is the change in log-odds of supporting Biden for a one-unit increase in
the predictor variable, which is essentially how much impact each
demographic characterstic has an effect on voting for Biden.

The confidence intervals tell us the range within we can be confident
that the true effect lies. Smaller confidence intervals means there is a
higher level of precision in the estimate of the effect size. I am not
as interested in the intervals that cross zero because that means that
there is data to support each side (Biden or Trump) and so they are less
statistically significant.

@@

The conclusions I can draw from Figure~\ref{fig-coefficient} align with
what I expected given the dataset. It's clear that higher education
levels, specifically 4-year degrees and post-grad degrees, are
positively associated with support for Biden. Higher age groups,
specifically 45-64 and 65+, are strongly tied to voting for Trump. Men
are less likely to vote for Biden than Women.

@@

Figures \textbf{?@fig-page}, \textbf{?@fig-pgender}, and
\textbf{?@fig-pedu} are recreations of the earlier graphs we saw
showcasing the proportion of voters for Joe Biden by groups within each
demographic, where the bar is the data from CCES 2020 while the point is
the prediction generated by the model.

@@

By observation, it is evident that the model's prediction was fairly
close to what the CCES data showed. The trend remains the same for each
result. However, gender and education were predicted to have a higher
sentiment of voting for Joe Biden while age had a lower sentiment.

It is worth nothing though that in Figure~\ref{fig-pactivity}, all age
categories showed polling data of above 50\% to vote for Biden. Now with
the lower average vote, the older age categories of ``45-64'' and
``65+'' are leaning towards Trump. On Figure~\ref{fig-pobesity} for the
lower education groups, the ``No-HS'' group which was at just about 50\%
is now above it, and the ``High School Graduate'' is also closer to
voting for Biden. While this may seem marginal, close elections where
voter sentiment is close to 50\% would be largely impacted by changes
like this. Although ultimately this is not an accurate predictor for who
would win the election, only which groups would vote for who.

@@

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-brfss}{}}%
{``4 Comparison of Data Sources Used to Assess Obesity Prevalence and
Trends.''} n.d. The National Academies of Sciences, Engineering,;
Medicine; \url{https://nap.nationalacademies.org/read/23505/chapter/7}.

\leavevmode\vadjust pre{\hypertarget{ref-Modelsummary}{}}%
Arel-Bundock, Vincent. 2021. \emph{Modelsummary: Summary Tables and
Plots for Statistical Models and Data: Beautiful, Customizable, and
Publication-Ready}.
\url{https://CRAN.R-project.org/package=modelsummary}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dataset}{}}%
Centers for Disease Control and Prevention (CDC), National Center for
Chronic Disease Prevention and Health Promotion, Division of Nutrition,
Physical Activity, and Obesity. 2023. {``{Nutrition, Physical Activity,
and Obesity - Behavioral Risk Factor Surveillance System}.''} Atlanta,
Georgia:
\url{https://chronicdata.cdc.gov/Nutrition-Physical-Activity-and-Obesity/Nutrition-Physical-Activity-and-Obesity-Behavioral/hn4x-zwk7};
{Centers for Disease Control and Prevention}.

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-cdcinitiatives}{}}%
{``Overweight \& Obesity \textbar{} CDC.''} n.d. Centers for Disease
Control; Prevention; \url{https://www.cdc.gov/obesity/index.html}.

>>>>

\KOMAoption{captions}{tableheading}
\usepackage{float} \floatplacement{figure}{H}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Americans who are wealthier and perform more strength training are less likely to be obese},
  pdfauthor={Victor Ma},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Americans who are wealthier and perform more strength training
are less likely to be obese\thanks{Code and data are available at:
https://github.com/bestmustard/activity-bmi}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{An analysis of how exercise habits and wealth correlate with
BMI}
\author{Victor Ma}
\date{March 16, 2024}

\begin{document}
\maketitle
\begin{abstract}
This study examines the correlation between varying levels of physical
activity,
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, boxrule=0pt, frame hidden, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

The data I am using is from the Center of Disease Control and Prevention
(CDC), a government-officiated service organization dedicated to health
research in the United States. In particular, this dataset contains
information on an adult's diet, physical activity, and weight status
from CDC's Behavioral Risk Factor Surveillance System- America's premier
system for collecting data about health-related risk behaviours
conducted through telephone surveys (Centers for Disease Control and
Prevention (CDC) 2023). I will be focusing on the variables of activity
level and level of income as explanatory variables in the logistic
regression model. The estimand will be the probability that an
individual is obese based on these factors.

@@

This analysis is conducted using R, using several R packages to
facilitate my analysis and presentation. This includes tidyverse for
data manipulation and visualization, knitr for report generation,
modelsummary for model interpretation, and rstanarm for Bayesian
regression modeling (R Core Team 2021; Xie 2021; Arel-Bundock 2021;
Goodrich et al. 2022; Kay 2021; Wickham et al. 2021). Some portions
including ggplot graphs and the ``Data'' and ``Discussion'' sections
were written with the help of ChatGPT4 OpenAI (2023).

@@

I used a dataset called ``Nutrition, Physical Activity, and Obesity -
Behavioral Risk Factor Surveillance System'' pulled directly from the
CDC website (Centers for Disease Control and Prevention (CDC) 2023). The
.csv file obtained from the website contains 93250 data points with the
relevant information of an individual's activity level based on their
survey response, BMI, and various demographics. The dataset is owned by
the Division of Nutrition, Physical Activity, Obesity (DNPAO), a
division under the CDC which focuses directly on preventing chronic
diseases by promoting better nutrition practices.

The CDC's Division of Nutrition, Physical Activity, and Obesity conducts
comprehensive surveillance and research to understand and address
obesity, focusing on policy and environmental strategies to promote
healthy eating and active living. The organization collects data from
the largest scale health survey systems in the United States, including
both the Behavioral Risk Factor Surveillance System (BRFSS) and the
National Health and Nutrition Examination Survey (NHANES) ({``Data \&
Statistics \textbar{} Overweight \& Obesity \textbar{} CDC,''} n.d.).

@@

The data used in this paper does not represent the full dataset, as data
points had to be removed for any missing responses. The previously more
robust dataset with 93250 data points was reduced to 10218 in this
process. The categories available for both the respondent variables do
not allow for some details, as the markers for physical activity were
very specific. Many individuals may not adhere directly to the possible
responses in the survey, and it is impossible to account for individuals
who perform more physical activity than the provided options. The income
levels also do not provide a broad perspective, with the maximum level
being \$75,000+. There is no evidence or rationale provided regarding
why these options were chosen.

@@

Figure~\ref{fig-activity} tells us that Americans who do not perform any
leisurely exercise are the most well represented, with all other groups
having an equal number of points in this data.

In Figure~\ref{fig-income}, oddly enough every income level was equally
represented in this study.

Below are some figures representing the proportion of people who were
considered obese based on their activity level and their wealth.

@@

Figure~\ref{fig-activityobesity} shows no correlation between obesity
and activity level. The proportion of people with obesity doing moderate
cardio is unexpected.

@@

We can see that in Figure~\ref{fig-incomeobesity}, obesity tended to
trend down with higher levels of income. \newpage

@@

\hypertarget{summary-interpretation}{%
\paragraph{Summary Interpretation}\label{summary-interpretation}}

Each coefficient in a logistic regression model quantifies the change in
the log odds of the outcome per unit change in the predictor. In this
context, with the probability of being obese as the outcome:

(Intercept) (5.329): When all other variables are at their baseline
levels (no physical activity and the lowest income category), the log
odds of being obese are 5.329.

activityCardio + Strength (-8.164): Engaging in both cardio and strength
activities is associated with an 8.164 unit decrease in the log odds of
being obese compared to the baseline of no activity.

activityDouble Cardio (-4.518): Doing 300 minutes of moderate cardio or
150 minutes of vigorous cardio results in a 4.518 unit decrease in the
log odds of being obese compared to the baseline.

activityNo Activity (-5.269): Having no leisure-time physical activity
is associated with a 5.269 unit decrease in the log odds of being obese
compared to the baseline. This negative value is unexpected, as we would
typically predict no activity to increase the odds of obesity unless the
baseline includes negative health behaviors even more associated with
obesity.

activityStrength (-5.092): Engaging only in strength training activities
is associated with a 5.092 unit decrease in the log odds of being obese
compared to the baseline.

income15-25 (0.096): Being in the \$15,000 to \$25,000 income bracket is
associated with a 0.096 unit increase in the log odds of being obese
compared to the reference income category.

income25-35 (-0.719): Being in the \$25,000 to \$35,000 income bracket
is associated with a 0.719 unit decrease in the log odds of being obese.

income35-50 (-0.990): Being in the \$35,000 to \$50,000 income bracket
is associated with a 0.990 unit decrease in the log odds of being obese.

income50-75 (-1.063): Being in the \$50,000 to \$75,000 income bracket
is associated with a 1.063 unit decrease in the log odds of being obese.

income75+ (-0.401): Being in the over \$75,000 income bracket is
associated with a 0.401 unit decrease in the log odds of being obese.

It is important to note that these are all associative relationships and
don't imply causation.

In order to better interpret the results of the model, I can create a
coefficient plot to visually see the effect sizes of the predictor
variables on the likelihood of an individual being obese.

Figure~\ref{fig-coefficient} maps each predictor variable on the y-axis
to an effect size and confidence interval on the x-axis. The effect size
is the change in log-odds of being obese for a one-unit increase in the
predictor variable, which is essentially how much impact each variable
has an effect on being obese

The confidence intervals tell us the range within we can be confident
that the true effect lies. Smaller confidence intervals means there is a
higher level of precision in the estimate of the effect size. I am not
as interested in the intervals that cross zero because that means that
there is data to support each side (obese and not obese) and so they are
less statistically significant.

@@

The conclusions I can draw from Figure~\ref{fig-coefficient} align with
what I expected given the dataset. We can see that generally, higher
incomes trend with a lower log-likelihood of being obese. The
conclusions drawn from the activity levels also are in line with what we
saw earlier on Figure~\ref{fig-activity}, though they are not at all
what I expected as I believed exercise to have a negative correlation
with obesity. I did not expect that the (Intercept) no

@@

Figures Figure~\ref{fig-pactivity} and Figure~\ref{fig-pobesity}, are
recreations of the earlier graphs we saw showcasing the proportion of
obesity by groups within categories, where the bar is the data from CDC
while the point is the prediction generated by the model.

@@

We can see that the model prediction resembled the CDC data by trend,
however for most of the categories within both
Figure~\ref{fig-pactivity} and Figure~\ref{fig-pobesity}, the prediction
for obesity was lower than the data suggested. Moderate cardio having
such a high proportion of obesity as unexpected.

@@

In this paper, we used real-world statistics on Americans' activity
levels, income, and whether or not they were considered obese to find a
correlation between these behavioural and socioeconomic factors and
obesity. What we found was that contrary to popular belief, our model
did not predict lower obesity levels for individuals who exercised more.
In particular, there was a large proportion of individuals who did
moderate cardio and were obese, but there was correlation with lower
obesity and strength training. Generally, higher income levels were also
associated with lower rates of obesity.

While this data may not be indicative of reality, the lack of
correlation between exercise and obesity may reveal truths about
societal beliefs in terms of how to get fit. Like myself, many Americans
grew up watching TV where commercial ad breaks would feature fad diets,
fast 10 minute work outs, and buzz phrases like ``do this for 30 minutes
a week to lose X lbs of fat!'' Fitness may be viewed with a dogmatic
stigma due to media portrayals which push the idea of a `hardcore'
lifestyle being required for a fit body.

Due to this, it is possible that individuals believe in exercise being a
greater factor for fat loss than nutrition. With the highest category of
300 minutes of moderate cardio used in CDC's survey, an adult weighing
160 lbs can expect to burn approximately 1825 calories in a week (Mayo
Clinic Staff 2021). As a single pound of body fat contains roughly 3500
calories, this would seem like half a pound of fat loss per week.
However, this does not account for the possibility that an individual
consumes more food with added physical activity, and 1825 calories
spread out over a week is obly 260 calories per day. That equates to
less than a small fries at McDonalds, or 2 or 3 eggs with oil.

It is impossible to predict how an individual's body composition will
change without knowing their nutritional information, specifically their
caloric intake. There are various reasons why higher incomes might trend
with lower obesity rates. People with higher incomes also tend to have
achieved higher levels of education, which may be tied to access of
information. They also have more access to help from professionals,
better training facilities, and more food options. The study ``Nutrition
quality of food purchases varies by household income: the SHoPPER
study'' published in BMC Public Health highlights that lower-income
households tend to purchase foods of lower nutritional quality compared
to higher-income households. This is due to financial constraints
limiting the purchase of healthier options like fruits and vegetables,
leading to a higher purchase of less healthful foods such as frozen
desserts or fast food. The study emphasizes that food purchasing
patterns significantly mediate income differences in dietary intake
quality (French et al. 2019).

@@

As outlined previously, the data points were self reported which could
lead to false data due to dishonesty or lack of care in measurement. The
dataset was also filtered to remove incomplete datapoints, resulting in
almost 90\% of the initial dataset being removed. The discrete
categories used for both physical activity and income may oversimplify
the spectrum of exercise habits which overlooks the nuances of
individual physical activity patterns. The income cap at \$75,000 also
fails to show variations in prevalence of obesity in higher income
brackets.

Future research should aim to incorporate objective measures of physical
activity, perhaps through wearable technology, to diminish
self-reporting biases. A broader dataset, possibly integrating direct
measures of physical activity and detailed nutritional intake, would
enable a more comprehensive analysis. Investigating the impact of higher
income brackets beyond \$75,000 and accounting for regional
cost-of-living differences could refine understanding of the
income-obesity relationship. Additionally, longitudinal data could shed
light on the temporal dynamics between exercise habits and BMI changes
over time.

Further, integrating geospatial analyses to assess environmental
factors, such as access to recreational spaces and healthy food outlets,
could add further context to obesity determinants. Given the
multifaceted nature of obesity, interdisciplinary studies combining data
from healthcare, urban planning, and social sciences could offer more
holistic insights. \newpage

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Modelsummary}{}}%
Arel-Bundock, Vincent. 2021. \emph{Modelsummary: Summary Tables and
Plots for Statistical Models and Data: Beautiful, Customizable, and
Publication-Ready}.
\url{https://CRAN.R-project.org/package=modelsummary}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dataset}{}}%
Centers for Disease Control and Prevention (CDC). 2023. {``{Nutrition,
Physical Activity, and Obesity - Behavioral Risk Factor Surveillance
System}.''} Atlanta, Georgia:
\url{https://chronicdata.cdc.gov/Nutrition-Physical-Activity-and-Obesity/Nutrition-Physical-Activity-and-Obesity-Behavioral/hn4x-zwk7};
{Centers for Disease Control and Prevention}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-nutritionquality}{}}%
French, Simone A., Christy C. Tangney, Melissa M. Crane, Yamin Wang, and
Bradley M. Appelhans. 2019. {``Nutrition Quality of Food Purchases
Varies by Household Income: The SHoPPER Study.''} \emph{BMC Public
Health} 19 (231).

@@

\leavevmode\vadjust pre{\hypertarget{ref-mayoclinic}{}}%
Mayo Clinic Staff. 2021. {``Exercise for Weight Loss: Calories Burned in
1 Hour.''}
\url{https://www.mayoclinic.org/healthy-lifestyle/weight-loss/in-depth/exercise/art-20050999}.

@@
